Wigglyhedra

### 2025-03-11 wigglyAligned/wigglyhedra.tex
expand Remark 33

\author{Vincent Pilaud}
\address{Universitat de Barcelona}
\email{vincent.pilaud@ub.edu}
\urladdr{\url{https://www.ub.edu/comb/vincentpilaud/}}

@@

\begin{remark}
\label{rem:wigglyLatticeAntiIsomorphism}
The map~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_n)$ obviously provides an anti-isomorphism of the wiggly lattice~$\wigglyLattice_n$.
\end{remark}

@@

@@

\begin{remark}
The map~$\Phi$ sends the wiggly complex automorphism of \cref{rem:wigglyComplexAutomorphism} given by the vertical reflection to the wiggly lattice anti-isomorphism of \cref{rem:wigglyLatticeAntiIsomorphism}.
\end{remark}

>>>>

\author{Vincent Pilaud}
\address[Vincent Pilaud]{Universitat de Barcelona \& Centre de Recerca Matemàtica, Barcelona, Spain}
\email{vincent.pilaud@ub.edu}
\urladdr{\url{https://www.ub.edu/comb/vincentpilaud/}}

@@

@@

\begin{remark}
\label{rem:wigglyLatticeAntiIsomorphism}
Let~$\varepsilon$ be the permutation of~$[2n]$ exchanging~$2j-1$ with~$2j$ for all~$j \in [n]$.
Then the maps~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_{2n})$ and~$\sigma_1 \dots \sigma_{2n} \mapsto \varepsilon(\sigma_{2n}) \dots \varepsilon(\sigma_1)$ are two obvious bijections on wiggly permutations of~$[2n]$. Moreover, the first map is an anti-isomorphism of the wiggly lattice~$\wigglyLattice_n$ (while the second map is not).
\end{remark}

@@

\begin{remark}
The map~$\Phi$ sends the wiggly complex automorphisms of \cref{rem:wigglyComplexAutomorphism} to the bijections on wiggly permutations of \cref{rem:wigglyLatticeAntiIsomorphism}. In particular, it sends the vertical reflection on wiggly pseudotriangulations to the wiggly lattice anti-isomorphism on wiggly permutations given by~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_{2n})$.
\end{remark}
